A Fast and Tight Heuristic for A* in Road Networks

### 2021-01-31 paper/ch_potentials.tex
add basic CH to table

\begin{table*}
\centering
\caption{
CH-Potentials performance for different route planning applications.
We report average running times and number of queue pushes.
We also report the average length increase, that is how much longer the final shortest distance is compared to the lower bound.
Finally, we report the average running time of Dijkstra's algorithm as a baseline and the speedup over this baseline.
}\label{tab:applications}
\input{table/applications.tex}
\end{table*}

Table~\ref{tab:applications} depicts the running times of CH-Potentials in the various applications, such as those described in Section~\ref{sec:extensions}.
Speedups compared to extensions of Dijkstra's algorithm for the respective application are depicted.
We start with the base case where $w_q = w_\ell$.
This is the problem variant solved by the basic CH algorithm (a CH query takes 0.163\,ms on average on this graph).
CH achieves query running times of 0.16\,ms on average.
CH-Potentials are roughly four times slower but still achieve a huge speedup over Dijkstra of 3243.
Such large speedups are typical for CH.
This shows that CH-Potentials gracefully converges toward a CH in the $w_q = w_\ell$ special case.

>>>>

\begin{table*}
\centering
\caption{
CH and CH-Potentials performance for different route planning applications.
We report average running times and number of queue pushes.
We also report the average length increase, that is how much longer the final shortest distance is compared to the lower bound.
Finally, we report the average running time of Dijkstra's algorithm as a baseline and the speedup over this baseline.
}\label{tab:applications}
\input{table/applications.tex}
\end{table*}

Table~\ref{tab:applications} mainly depicts the running times and CH-Potentials in the various applications, such as those described in Section~\ref{sec:extensions}.
For comparison, we also report CH running times.
A basic CH can only handle the $w_q = w_\ell$ case.
Speedups compared to extensions of Dijkstra's algorithm for the respective application are depicted.
We start with the base case where $w_q = w_\ell$.
This is the problem variant solved by the basic CH algorithm (a CH query takes 0.163\,ms on average on this graph).
CH achieves query running times of 0.16\,ms on average.
CH-Potentials are roughly four times slower but still achieve a huge speedup over Dijkstra of 3243.
Such large speedups are typical for CH.
This shows that CH-Potentials gracefully converges toward a CH in the $w_q = w_\ell$ special case.
